Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-26 manuscript/manuscript.Rmd

@@

In Fig. \ref{fig:state-space}, we perform a back to back visualization of all the policies evaluated up to now---MSY constant mortality, 80% MSY constant mortality, DRL and escapement.
This highlights the similarity between the policy found by the DRL agent and the optimal escapement policy.

@@

```{r state-space, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))

>>>>

```{r}
#| label: textbox
#| out.width: "1\\linewidth"

knitr::include_graphics("figures/textbox.png")
```

@@

In Fig. \ref{fig:state-space}, we perform a back to back visualization of all the policies evaluated up to now---MSY constant mortality, 80% MSY constant mortality, DRL and escapement.
The policies are computed at each state along the paths they traverse in the 50 evaluation rounds, and the values are projected on the $X$-$Z$ plane for visualization.
This figure highlights the similarity between the policy found by the DRL agent and the optimal escapement policy.

Notice the anti-correlation between $X$ and $Y$ along the paths, this is especially prominent for the constant mortality plots.
This anti-correlation is, furthermore, observed in the time series plots (see Fig. \ref{fig:timeseries} and App. \ref{app:tbd}).

```{r}
#| label: state-space
#| fig.cap: "Policy heatmaps. Each policy, say, $\\pi$, was evaluated at points $(x,y,z)$ visited during any of the 50 evaluation rounds. We projected this data down to the $X$-$Y$ plane---i.e. we plotted the heatmap $\\pi(x,y,z)$ as a function of $x$ and $y$."
#| out.width: "6.5in"
i_tac <- which.min(abs(actions - best_action * 0.8))

pmsy <- msy_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == best_action) |>
  ggplot(aes(X, Y, color = harvest)) +
  geom_point() + sc +
  xlim(0,1) +
  ylim(0,0.85) +
  ggtitle("Opt. Const. Mortality")

ptac <- msy_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  filter(action == actions[[i_tac]]) |>
  ggplot(aes(X, Y, color = harvest)) +
  geom_point() + sc +
  xlim(0,1) +
  ylim(0,0.85) +
  ggtitle("80% Opt. Const. Mortality")

pppo <- ppo_df |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, harvest = action * X) |>
  ggplot(aes(X, Y, color = harvest)) +
  geom_point() + sc +
  xlim(0,1) +
  ylim(0,0.85) +
  ggtitle("DRL")

pesc <- opt_escapement |>
  mutate(X = X+1, Y = Y+1, Z = Z+1, 
        harvest = case_when(
          X - escapement > 0 ~ X - escapement,
          X - escapement <= 0 ~  0)
         ) |> 
  ggplot(aes(X, Y, color = harvest)) +
  geom_point() + sc +
  xlim(0,1) +
  ylim(0,0.85) +
  ggtitle("Opt. Const. Escapement")

@@

```{r state-space_old, fig.cap="TBD.", out.width = "6.5in"}
i_tac <- which.min(abs(actions - best_action * 0.8))
